Embedding characterization-- fixing a report

### 2019-11-19 notes/bo-separated.tex
Added my questions to Bo's notes

\begin{lemma} \label{lemma:U-surject}
  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
  We write $R_U$ for the value of this map at $U$.
\end{lemma}
\begin{proof}
  For each report $r$, write $u_r$ for its embedding point and for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
  Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
  \jessiet{Doesn't $U$ correspond to $\Gamma$ and $R$ to $\gamma$?}
  By definition of embedding, we have $u_r \in \gamma(p) \iff r \in \Gamma(p)$.
  So if $U = \gamma(p)$, we must have $R = \Gamma(p)$.
  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
\end{proof}

@@

>>>>

\begin{lemma} \label{lemma:U-surject}
  There is a surjection from $\mathcal{U}$ to $\mathcal{S}$ where $U \mapsto R$ if, for some $p$, we have $\gamma(p) = U$ and $\Gamma(p) = R$.
  We write $R_U$ for the value of this map at $U$.
\end{lemma}
\begin{proof}
  For each report $r$, write $u_r$ for its embedding point and for each $U \in \mathcal{U}$, let $R_U = \{r : u_r \in U\}$.
  Recall that $\mathcal{U}$ is the collection of sets $U = \gamma(p)$ for some $p$, while $\mathcal{S}$ is the collection of sets $R = \Gamma(p)$ for some $p$.
  By definition of embedding, we have for any $p$ that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  So if $U = \Gamma(p)$, we must have $R_U = \gamma(p)$.
  This shows that $R_U \in \mathcal{S}$ for all $U$, and furthermore, the map is surjective because every $R \in \mathcal{S}$ is equal to $R_U$ for some $U \in \mathcal{U}$.
\end{proof}

@@

(Bo, 2019-11-13)

\begin{theorem}
  Let $L(\cdot;p)$ be a polyhedral function with $U^* := \arg\min_{u} L(u;p)$.
  Then there exists $c > 0$ such that $L(u;p) \geq c \cdot \|U^* - u\|_2$ for all $u$.
\end{theorem}
\begin{proof}
  Consider the epigraph of $L(\cdot;p)$, a polyhedral set (intersection of finitely many halfspaces).
  Recall that each face of the epigraph is uniquely identified by a subset of constraints which are tight for exactly that face.
  In particular, $U^*$ is a face (as it is the set of points exposed by the ``downward'' direction), identified by some subset $S$.

  Now consider all faces that are proper subsets of $U^*$; they are identified by all supersets $S' \supsetneq S$ of constraints.
  We claim $U^*$ is the union of the relative interiors of these faces.

  [To be continued...]
\end{proof}
